---
title: "my_rf_cv"
author: "Judy Tian"
date: "6/9/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Tutorial for `my_rf_cv`

``` {r, message=FALSE}
library(readr)
library(ggplot2)
library(magrittr)
library(dplyr)
library(randomForest)
library(kableExtra)
source("../Code/my_rf_cv.R")
# Get all data from local subfolder
my_penguins <- read_csv("../Data/my_penguins.csv")
my_gapminder <- read_csv("../Data/my_gapminder.csv")

cv_num <- matrix(NA, 30, 3)
sd_cv <- rep(NA, 3)
a <- 1

# Iterate through k in (2, 5, 10)
for (i in c(2, 5, 10)) {
  # For each value of k, run function 30 times
  for (j in 1:30) {
    # Call my function tp get CV estimated MSE
    cv_num[j, a] <- my_rf_cv(i)
  }
  sd_cv[a] <- sd(cv_num[, a])
  a <- a + 1
}
# Build data frame of output
out1 <- data.frame("k" = "2", "result" = cv_num[, 1])
out2 <- data.frame("k" = "5", "result" = cv_num[, 2])
out3 <- data.frame("k" = "10", "result" = cv_num[, 3])
cv_result <- rbind(out1, out2, out3)
# Plot 3 boxplots to display data
ggplot(data = cv_result, aes(x = factor(k), y = result, fill = k)) + 
  geom_boxplot() +
  labs(x = "k",
       y = "CV MSE",
       title = "3 boxplots of CV MSE from 30 simulations") +
  theme(plot.title = element_text(hjust = 0.5))
# Save graph
ggsave(filename = "boxplot.png", path = "../Output/Figures")

# Build table to display the values.
cv_table <- data.frame("mean" = colMeans(cv_num), 
                       "sd" = sd_cv)
cv_table <- kable_styling(kable(cv_table))

# Save table of summary statistics
saveRDS(cv_table, "../Output/Results/summary_table.rds")
# Save simulation results
cv_num <- data.frame(cv_num)
colnames(cv_num) <- c("2", "5", "10")
write_csv(cv_num, path = "../Output/Results/simulation_results.csv")
```

From the boxplot graph, we could see as `k` increases, the cross-validation error's median decreases and width decreases.

Also, from the table, we could see as `k` increases, the cross-validation error's mean decreases and the standard deviation decreases.

Those two indicates the same thing -- as `k` increases, test is more accurate. This makes sense since the rule of thumb, `k = 5` and `k = 10` tend to result in an ideal balance in terms of the bias-variance tradeoff.
